% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.
 
%!TEX root =  

\chapter[Message Reference]{Message Reference}

\section{Introduction}

The following information is provided for each of the messages:

\underline{Description:}

Description of the message's function.

\underline{Protocol:}

Which protocol the message belongs to. Only messages that relate to refresh slots belong to a protocol.

\underline{Group:}

Which message size group the message belongs to.

\underline{Opcode:}

The opcode mnemonic. This is the Digitrax assigned mnemonic when known.

\underline{Type:}

The message type - \gls{Broadcast}, \gls{Command}, \gls{Response}, or \gls{Report}.

\underline{Encoding:} 

How the message is encoded byte by byte.

\underline{Response:} 

The response expected from a command message, if applicable.

\underline{Signature:}

The bits and bytes that must be tested to determine the message's unique type.

\underline{Notes:} 

Any notes.

\input{Chapter1-Ack}
\input{Chapter1-Busy}
\input{Chapter1-CfgSlotDataP1}
\input{Chapter1-CfgSlotDataP2}
\input{Chapter1-ConsistDirF0F4}
\input{Chapter1-GetBrdOpSw}
\input{Chapter1-GetCfgSlotDataP1}
\input{Chapter1-GetCfgSlotDataP2}
\input{Chapter1-GetInterfaceData}
\input{Chapter1-GetLocoSlotDataLAdrP1}
\input{Chapter1-GetLocoSlotDataLAdrP2}
\input{Chapter1-GetLocoSlotDataP1}
\input{Chapter1-GetLocoSlotDataP2}
\input{Chapter1-GetLocoSlotDataSAdrP1}
\input{Chapter1-GetLocoSlotDataSAdrP2}
\input{Chapter1-GetSwState}
\input{Chapter1-IllegalMoveP1}
\input{Chapter1-IllegalMoveP2}
\input{Chapter1-IMMPacket}
\input{Chapter1-InterfaceData}
\input{Chapter1-IPLDataLoad}
\input{Chapter1-IPLDevData}
\input{Chapter1-IPLDiscover}
\input{Chapter1-IPLEndLoad}
\input{Chapter1-IPLSetAddr}
\input{Chapter1-IPLSetupBL2}
\input{Chapter1-LinkSlotsP1}
\input{Chapter1-LinkSlotsP2}
\input{Chapter1-LocoBinStateP2}
\input{Chapter1-LocoDirF0F4P1}
\input{Chapter1-LocoDirF0F4P2}
\input{Chapter1-LocoF0F6P2}
\input{Chapter1-LocoF5F8P1}
\input{Chapter1-LocoF7F13P2}
\input{Chapter1-LocoF5F11P2}
\input{Chapter1-LocoF12F20F28P2}
\input{Chapter1-LocoF13F19P2}
\input{Chapter1-LocoF14F20P2}
\input{Chapter1-LocoF21F27P2}
\input{Chapter1-LocoF21F28P2}
\input{Chapter1-LocoSlotDataP1}
\input{Chapter1-LocoSlotDataP2}
\input{Chapter1-LocoSpdP1}
\input{Chapter1-LocoSpdP2}
\input{Chapter1-LocoSpdDirP2}
\input{Chapter1-NoFreeSlotsP1}
\input{Chapter1-NoFreeSlotsP2}
\input{Chapter1-MoveSlotsP1}
\input{Chapter1-MoveSlotsP2}
\input{Chapter1-PeerXfer16}
\input{Chapter1-ProgCV}
\input{Chapter1-ProgSlotDataP1}
\input{Chapter1-PwrOff}
\input{Chapter1-PwrOn}
\input{Chapter1-Reset}
\input{Chapter1-SensRepGenIn}
\input{Chapter1-SensRepTurnIn}
\input{Chapter1-SensRepTurnOut}
\input{Chapter1-SetBrdOpSw}
\input{Chapter1-SetIdleState}
\input{Chapter1-SetLocoSlotDataP1}
\input{Chapter1-SetLocoSlotDataP2}
\input{Chapter1-SetLocoSlotStat1}
\input{Chapter1-SetSwState}
\input{Chapter1-SetSwStateWithAck}
\input{Chapter1-SlotNotImplemented}
\input{Chapter1-SVProg}
\input{Chapter1-SwState}
\input{Chapter1-TransRep}
\input{Chapter1-UnlinkSlotsP1}
\input{Chapter1-UnlinkSlotsP2}

